|

### 2021-05-03 documentation/paper.Rmd
Added Mark's suggested revision on data

The PollBase data come from a range of sources. This includes books published after each general election, polling almanacs, data shared amongst academics and pollsters, contemporary media reports, and figures from polling company websites. The data since the 1983 general election are complete, baring any individual errors. Likewise, data are complete for every general election campaign before 1979. The coverage between elections is more comprehensive for some pollsters than others^[We encourage any readers who might know of polls missing from the PollBase dataset to contact its author via his website (https://www.markpack.org.uk)]. Gallup and NOP data, in particular, are well-covered as the two companies have collated and published their results. The PollBase data start on `r format(min(pollbase$start), "%d %B %Y")`. Yet, consistent polling began only after the 1955 general election. Thus, we take it as our starting point.

@@

kable(
  pbp_head,
  align = "ccccccc",
  format = "latex",
  label = "head-tab",
  booktabs = TRUE,
  escape = FALSE,
  caption = paste0("The first 5 rows of the PollBasePro dataset")
  ) %>% 
  kable_styling(position = "center")

>>>>

The PollBase data come from a wide range of sources. This includes books published after each general election, polling almanacs, data shared amongst academics and pollsters, contemporary media reports, and figures from polling company websites. The data since the 1983 general election are complete, baring possible but rare individual errors. Prior to 1983, the data is likewise complete for each general election campaign period. For periods between general elections prior to 1983, coverage is more comprehensive for some pollsters than others^[We encourage any readers who might know of polls missing from the PollBase dataset to contact its author via his website (https://www.markpack.org.uk)]. Gallup and NOP data, in particular, are well-covered as the two companies have collated and published their results. The PollBase data start in `r format(min(pollbase$start), "%B %Y")`. However, we take as our starting point the 1955 Parliament given the gaps in the earlier data.

@@

kable(
  pbp_head,
  align = "ccccccc",
  format = "latex",
  label = "head-tab",
  booktabs = TRUE,
  escape = FALSE,
  linesep = "",
  caption = paste0("The first 5 rows of the PollBasePro dataset")
  ) %>% 
  kable_styling(position = "center")
